---
title: "Tidy Models Tutorial"
author: "Rica Rebusit"
date: "3/20/2022"
output:
  html_document:
    theme: darkly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Get set up
This blog post is a tutorial to teach you how to fit a simple linear regression using **tidymodels**. So first, you will need to install the tidymodels package by typing **install.packages("tidymodels")** in the console. If you don't have it already, you will also need to install the **ggplot2** and **dplyr** packages. Now that you have those packages installed, you will now want to load it in by typing **library()**
```{r}
library(tidymodels)
library(ggplot2)
library(dplyr)
```
Let's load the data. You can get it from here: [Abalone Data Set](https://www.kaggle.com/datasets/rodolfomendes/abalone-dataset)
```{r}
abalone <- read.csv("~/Documents/RicaRebusitWeb/abalone.csv")
head(abalone)
```

## Making the linear regression
With this data set we can try to find the relationship of our response variable **Rings** which represents age and a predictor, let's choose  **Diameter**. Make a scatter plot of these variables.
```{r}
ggplot(abalone, aes(Diameter, Rings)) + geom_point()
```

Create a parsnip for the model. This provides tidy, unified interface.
```{r}
par.spec <- linear_reg() %>%
  set_mode("regression") %>%
  set_engine("lm")
```
Now we can fit a model **y~x** on our response variable **Rings** as y and predictor variable **Diameter** as x
```{r}
lm.fit <- par.spec %>% # The specification from the previous step
  fit(Rings ~ Diameter, data=abalone)
lm.fit
```
We can now use this model to look at various aspects such as the parameters using **tidy()**, the statistics using **glance()**, and the predictions using **predict()**
```{r}
tidy(lm.fit)
glance(lm.fit)
predict(lm.fit, new_data=abalone)
```

If you want to look at the predictions of Rings you can make a tibble of **Rings** and **.pred** the predictions
```{r}
bind_cols(
  predict(lm.fit, new_data=abalone), abalone
) %>%
  select(Rings, .pred)
```
And there you have it! A simple quick run through of a simple linear regression using **tidymodels**
